\bibitem{sPHENIXproposal}A. Adare et al. \textit{An Upgrade Proposal from the PHENIX Collaboration}. arXiv:1501.06197, 2015.

\bibitem{1} sPHENIX Conceptual Design Report. 2017.

\bibitem{2} Jinrui Huang, Zhong-Bo Kang, and Ivan Vitev. \textit{Inclusive b-jet production in heavy ion collisions at the LHC}. Phys. Lett., B726:251–256, 2013.

\bibitem{3} S. S. Cao, G.Y. Qin, and S. A. Bass. \textit{Energy loss, hadronization and hadronic interactions of heavy flavors in relativistic heavy-ion collisions}. Phys. Rev., C92:024907, 2015.

\bibitem{4} Min He, Rainer J. Fries, and Ralf Rapp. \textit{Heavy-Quark Diffusion and Hadronization in Quark-Gluon Plasma}. Phys. Rev., C86:014903, 2012.

\bibitem{5} T. Song, H. Berrehrah, J. M. Torres-Rincon, L. Tolos, D. Cabrera, W. Cassing, and E. Bratkovskaya. \textit{Single electrons from heavy-flavor mesons in relativistic heavy-ion collisions}. Phys. Rev., C96:014905, 2017.

\bibitem{6} J.C. Xu, J.F. Liao, and M. Gyulassy. \textit{Bridging soft-hard transport properties of quark-gluon plasmas with cujet 3.0}. JHEP, 1602:169, 2016.

\bibitem{7}  L. Adamczyk et al. \textit{Measurement of D0 Azimuthal Anisotropy at Midrapidity in Au+Au Collisions at psNN=200GeV}. Phys. Rev. Lett., 118(21):212301, 2017.


\bibitem{8} G. Contin, L. Greiner, J. Schambach, M. Szelezniak, et al. \textit{The STAR MAPS-based PiXeL detector}. arXiv:1710.02176, 2017. 72.

\bibitem{9} B Abelev et al. \textit{Technical Design Report for the Upgrade of the ALICE Inner Tracking System}. J. Phys., G41:087002, 2014.

\bibitem{10} M. Mager. A\textit{LPIDE, the Monolithic Active Pixel Sensor for the ALICE ITS upgrade.} Nucl. Instrum. Meth., A824:434–438, 2016.