\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage{lib/report-template}
\usepackage[all]{background}
\usepackage{lipsum}

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}

\SetBgContents{Preliminary version/1.0}% Set contents
\SetBgPosition{-0.5cm,-5.0cm}% Select location
\SetBgOpacity{1.0}% Select opacity
\SetBgAngle{90.0}% Select rotation of logo
\SetBgScale{2.0}% Select scale factor of logo


%Line spacing
\renewcommand{\baselinestretch}{1.5}

\title{projeto ATLAS}

\date{August 2019}


\begin{document}

\include{lib/frontpage}
%\include{lib/facepage}
\include{parts/resumo}
\include{parts/abstract}

\tableofcontents

\include{parts/introducao2}
\include{parts/objetivos}
\include{parts/desafios_cientificos_tecnologicos}
%\include{parts/cronograma}
\include{parts/disseminacao}
%\include{parts/outros_apoios}
\newpage
\begin{thebibliography}{9}



\bibitem{ref1} B. A. et al. (ALICE Collaboration), Technical design report for the upgrade of the alice time projection chamber, CERN-LHCC-2013-020
A886 (2013), http://cds.cern.ch/record/1622286.


\bibitem{tpcNIM} M.M. Aggarwal, et al., Nucl. Instrum. Meth. A 903, (2018) 215–223. 

\bibitem{discharge_paper} A. Deisting, et al., Nucl. Instrum. Meth. A 937, (2019) 168–180.

%
\bibitem{GSI_REPO} Garabatos C., et al., Stability test of ALICE TPC GEM chambers at the LHC, GSI FAIR SCIENTIFIC REPORT 2017, DOI:10.15120/GSI-2017-01856.
%

\bibitem{THGEM} H. Natal da Luz, et al., EPJ Web of Conferences 174, (2018) 01012.

\bibitem{book1} G. Lutz, Semiconductor Radiation Detectors: Device Physics, Springer-Verlag, Berlin Heidelberg, 2007. 

\bibitem{book2} H. Spieler, Semiconductor Detector Systems, Oxford University Press, Great Britain, 2005.


\bibitem{NIM} G. G. A. de Souza and  H. Natal da Luz, Nucl. Inst. Meth. A 937, (2019) 141–147.

\bibitem{xray} G.G.A. de Souza and H.N. da Luz, X-Ray Spectrometry 48, 5 (2018).

\bibitem{sirius} https://www.lnls.cnpem.br/sirius/livro-projeto-sirius/


\end{thebibliography}


\end{document}
